Spatial Analysis: Design-Based vs Model-Based

### 2021-01-29 draft.Rnw
minor updates

\begin{enumerate}
  \item Spatial Design-Based vs Spatial Model-Based: There are no comparisons in the literature between spatial model-based approaches and *spatially balanced* design approaches. From what we have seen, these comparisons are between spatial model-based approaches and independent random sample designs. While important to study this behavior, this comparison is no longer fair nor modern. Spatially balanced sampling has exploded in popularity throughout the last decade, and the design-based vs model-based literature needs to reflect this trend.
  \item A ``fair'' comparison: We feel that literature in this area has considered scenarios that are more well-suited for the model-based scenario. For example, if you simulate a Gaussian erorr with an exponential covariance and then then compare design-based estimates to model-based estimates assuming an exponential covariance, of course the model-based approach will outperform design-based approaches. And these are the types of comparisons in the literature, which find model-based approaches generally yield more precise variance estiamtes. A challenge lies in creating a comparison scenario that is reasonable and intuitive. One this to consider would be exploring the comparison after estimating a misspecified covariance function using model-based approaches. 
  \item Finite AND infinite populations: Literature in the area focuses specifically on finite populations or infinite populations; we want to discuss both in detail.
  \item Pragmatic Focus: We see papers in this area tend to be fairly technical. We want the focus to be less on details, more on discussing the pragmatic questions practitioners will be faced with. For example, a thorough discussion of benefits and drawbacks of each method written for practicioners is warranted.
  \item Provide reliable software

>>>>

\begin{enumerate}
  \item Spatial Design-Based vs Spatial Model-Based: There are no comparisons in the literature between spatial model-based approaches and *spatially balanced* design approaches. From what we have seen, these comparisons are between spatial model-based approaches and independent random sample designs. While important to study this behavior, this comparison is no longer fair nor modern. Spatially balanced sampling has exploded in popularity throughout the last decade, and the design-based vs model-based literature needs to reflect this trend.
  \item A ``fair'' comparison: We feel that literature in this area has considered scenarios that are more well-suited for the model-based scenario. For example, if you simulate a Gaussian erorr with an exponential covariance and then then compare design-based estimates to model-based estimates assuming an exponential covariance, of course the model-based approach will outperform design-based approaches. And these are the types of comparisons in the literature, which find model-based approaches generally yield more precise variance estiamtes. A challenge lies in creating a comparison scenario that is reasonable and intuitive. One this to consider would be exploring the comparison after estimating a misspecified covariance function using model-based approaches. 
  \item Finite AND infinite populations: Literature in the area focuses specifically on finite populations or infinite populations; we want to discuss both in detail.
  \item Pragmatic Focus: We see papers in this area tend to be fairly technical. We want the focus to be less on details, more on discussing the pragmatic questions practitioners will be faced with. For example, a thorough discussion of benefits and drawbacks of each method written for practicioners is warranted.
  \item Provide reliable software and code: Current literature presents the ideas but do not provide adequate access to user-friendly software amd cpde. We would clearly explain how to use `spsurvey` to design and analyze spatial probability samples and `sptotal` for FBPK. We would make a GitHub repository for the paper walking through code used throughout the manuscript.
